Improved association in a classical density functional theory for water

### 2014-01-17 papers/water-saft/paper.tex

Finally, in order to compare with experimental results, we examined
the hydration of Krypton.  We use a Lennard-Jones potential with
values $\epsilon = .9518$\fixme{units} and $\sigma = 3.42 \AA$ with mixing rules
and values from\cite{paschek2004temperature} where the water
parameters are based on SPC calculations. Figure~\ref{fig:g-Kr} shows a
comparison of the krypton-oxygen partial radial
distribution($g_{Kr-O}$) from the functional in this work and on
created from the functional of \hughesetal\ with experiment
\cite{bowron1998hydrophobic}.  The new functional shows an improvement
in the height of the first peak, and the general shape of $g_{O-Kr}$
compare to that of \hughesetal \

>>>>

Finally, in order to compare with experimental results, we examined
the hydration of Krypton.  We use a Lennard-Jones potential with
values $\epsilon = .9518$\fixme{units} and $\sigma = 3.42 \AA$ with mixing rules
and values from \cite{paschek2004temperature} where the water
parameters are based on SPC calculations. Figure~\ref{fig:g-Kr} shows a
comparison of the krypton-oxygen partial radial
distribution($g_{Kr-O}$) from the functional in this work and on
created from the functional of \hughesetal\ with experiment
\cite{bowron1998hydrophobic}.  The new functional shows an improvement
in the height of the first peak, and the general shape of $g_{O-Kr}$
compare to that of \hughesetal \
